---
title: "Feature Selection TSLA"
output: html_document
date: "2025-04-10"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

```


This file contains code blocks for feature engineering for TSLA only.

Ensure that Extract_FA_TSLA.ipynb, Technical Analysis.ipynb (TSLA), and TSLA_twitter_sentiment.csv were executed/downloaded before proceeding here.  


Install the following libraries:
install.packages(c("car", "dplyr", "glmnet", "caret"))
```{r Import librarires}

library(car)
library(dplyr)
library(glmnet)
library(caret)

```



Import datasets. Change file directory accordingly. Run the follow cell once.
```{r Import datasets}

merged_df_TSLA = read.csv("/Users/tanyikchen/Library/CloudStorage/OneDrive-UniversityofNottinghamMalaysia/y3/DIA/Datasets/TSLA_TA_FA.csv")

TSLA_SA = read.csv('/Users/tanyikchen/Library/CloudStorage/OneDrive-UniversityofNottinghamMalaysia/y3/DIA/Datasets/TSLA_twitter_sentiment.csv')

merged_df_TSLA = merged_df_TSLA[-c(1, 2), ]

```



Reformat data columns. Ensure every variable is in the correct format.
```{r Change data format}

merged_df_TSLA = merged_df_TSLA %>%
  rename(Date = Price)

merged_df_TSLA$Date = as.Date(merged_df_TSLA$Date, format="%Y-%m-%d")

merged_df_TSLA$Close = as.numeric(merged_df_TSLA$Close)
merged_df_TSLA$High = as.numeric(merged_df_TSLA$High)
merged_df_TSLA$Low = as.numeric(merged_df_TSLA$Low)
merged_df_TSLA$Open = as.numeric(merged_df_TSLA$Open)
merged_df_TSLA$Volume = as.numeric(merged_df_TSLA$Volume)

merged_df_TSLA$EPS = as.numeric(merged_df_TSLA$EPS)
merged_df_TSLA$P.E = as.numeric(merged_df_TSLA$P.E)
merged_df_TSLA$ROE = as.numeric(merged_df_TSLA$ROE)
merged_df_TSLA$D.E = as.numeric(merged_df_TSLA$D.E)
merged_df_TSLA$P.B = as.numeric(merged_df_TSLA$P.B)
merged_df_TSLA$Revenue_Growth = as.numeric(merged_df_TSLA$Revenue_Growth)
merged_df_TSLA$Gross_Margin = as.numeric(merged_df_TSLA$Gross_Margin)
merged_df_TSLA$B.S = as.numeric(merged_df_TSLA$B.S)

final_TSLA_df = merge(merged_df_TSLA, TSLA_SA, by = "Date", all.x = TRUE)

rf_data = final_TSLA_df[, !(names(final_TSLA_df) %in% c("Date", "Open", "High", "Low", "Volume"))]
rf_data = rf_data[-nrow(rf_data), ]

```



Feature selection using linear regression. Iteratively remove features with high VIF score. Stop removing features if the highest VIF score is less than 5.

SA is included in the study to study model performance after adding SA.
```{r Linear Regression feature selection}

#full_model = lm(Close ~ Daily_ROI + OBV + ATR + MACD + ADX + EPS + Revenue_Growth + Gross_Margin + P.E + ROE + D.E + P.B + B.S + sentiment_score, data = merged_df_TSLA)

model1TSLA = lm(formula = Close ~ Daily_ROI + OBV + ATR + MACD + ADX + EPS + Gross_Margin + sentiment_score, data = rf_data)

predictor_vars = attr(terms(model1AMZN), "term.labels")

summary(model1TSLA)
vif_values = vif(model1TSLA)
vif_values[order(vif_values, decreasing = TRUE)]

```



ANOVA test to check whether adding TA/FA/SA helps improve the model or not.
```{r ANOVA}

model_TSLA_TA = lm(Close ~ Daily_ROI + OBV + ATR + MACD + ADX, data = rf_data)
model_TSLA_FA = lm(Close ~ EPS + Gross_Margin, data = rf_data)
model_TSLA_TA_FA = lm(Close ~ Daily_ROI + OBV + ATR + MACD + ADX + EPS + Gross_Margin, data = rf_data)
model_TSLA_TA_FA_SA = lm(Close ~ Daily_ROI + OBV + ATR + MACD + ADX + EPS + Gross_Margin + sentiment_score, data = rf_data)

anova(model_TSLA_TA, model_TSLA_TA_FA)
anova(model_TSLA_FA, model_TSLA_TA_FA)
anova(model_TSLA_TA_FA, model_TSLA_TA_FA_SA)

```



Export data. Change output_path to desired file directory. This dataset will be input into the LSTM/PPO model.
```{r export data}

output_path = '/Users/tanyikchen/Library/CloudStorage/OneDrive-UniversityofNottinghamMalaysia/y3/DIA/Datasets/TSLA_Significant.csv'

all_vars = c("Date", "Close", predictor_vars)

merged_df_TSLA_new = final_TSLA_df[, names(final_TSLA_df) %in% all_vars]

write.csv(merged_df_TSLA_new, output_path)

```
